Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-22 supplement.tex
Reorder supplement sections; add text to MultiDecect-contributions section

\medskip
\begin{center}
\large Stefan Hammer, Wei Wang, Sebastian Will and Yann Ponty
\end{center}
\section{Approximate counting and random generation}
In fact, not only is $\#{\sf BIS}$ a reference problem in counting complexity, but it is also a landmark problem with respect to the complexity of approximate counting problems. In this context, it is the representative for a class of $\#{\sf BIS}$-hard problems~\citep{Bulatov2013} that are easier to approximate than $\# {\sf SAT}$, yet are widely believed not to admit any Fully Polynomial-time Randomized Approximation Scheme. Recent results reveal a surprising dichotomy in the behavior of $\#{\sf BIS}$: it admits a Fully Polynomial-Time Approximation Scheme (FPTAS) for graphs of max degree $\le 5$~\citep{Weitz2006}, but is as hard to approximate as the general $\#{\sf BIS}$ problem on graphs of degree $\ge 6$~\citep{Cai2016}. In other words, there is a clear threshold, in term of the max degree, separating (relatively) easy instances from really hard ones.

@@

    \begin{figure*}[t]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. By
        targeting the respective free energies $(-40,-40,-20)$ and
        $(-20,-20,-20)$ for the target structures (annotated in red and
        blue, resepectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure; moreover, for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogenous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{fig:energydist}
\end{figure*}

@@

\section{Contribution of terms to the MultiDefect score}
\label{sec:improvements}
\begin{figure}[h!]
\includegraphics[width=.48\textwidth]{Figs/statistics-Term1}
\includegraphics[width=.48\textwidth]{Figs/statistics-Term2}
\caption{Break-down of average MultiDefect values into their two components.}
\end{figure}

>>>>

\medskip
\begin{center}
\large Stefan Hammer, Wei Wang, Sebastian Will and Yann Ponty
\end{center}

\begin{figure}[tb]
      \begin{center}
        %{\sf \bfseries A}\includegraphicstop[width=0.32\textwidth]{Figs/offset2}\hspace{.5cm}
        %{\sf \bfseries B}
        \includegraphicstop[width=0.8\textwidth]{Figs/energy_distribution}
      \end{center}
      \caption{%
        Targeting specific energies using multi-dimensional Boltzmann
        sampling. We show the Turner energy distributions for
        three target structures R1, R2 and R3. By
        targeting the respective free energies $(-40,-40,-20)$ and
        $(-20,-20,-20)$ for the target structures (annotated in red and
        blue, resepectively), we demonstrate the
        effectivity of our adaptive multi-dimensional Boltzmann sampling
        procedure; moreover, for comparison, the distributions for uniform
        (U) and Boltzmann (B) samples---respectively associated with
        homogenous weights $1$ and $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{fig:energydist}
\end{figure}

\section{Contribution of terms to the MultiDefect score}

Figure~\ref{fig:contribtions-multidefect} breaks down the multi-defect
score of Eq.~$(\ref{eq:blueprintobjective})$, which is used to
evaluate the quality of multi-target designs. Recall that the total
score is composed of the term $\frac{1}{k} \sum_{\ell=1}^{k} (E(S,
R_\ell) - \EnsE(S))$, which evaluates the distances of the energies of
target structures to the minimum free energy (Distance to MFE), and
the term $\frac{1}{2\binom{k}{2}} \sum\limits_{1\leq\ell<j\leq
  k}|E(S,R_\ell) - E(S,R_j)|$, which evaluates the similarity of the
target structure energies of the target structures (Heterogeneity).

\label{appsec:multidefect}
\begin{figure}[h!]
\includegraphics[width=.48\textwidth]{Figs/statistics-Term1}
\includegraphics[width=.48\textwidth]{Figs/statistics-Term2}
\caption{Break-down of average MultiDefect values into their two components.}
\label{fig:contribtions-multidefect}
\end{figure}

\section{Approximate counting and random generation}
In fact, not only is $\#{\sf BIS}$ a reference problem in counting complexity, but it is also a landmark problem with respect to the complexity of approximate counting problems. In this context, it is the representative for a class of $\#{\sf BIS}$-hard problems~\citep{Bulatov2013} that are easier to approximate than $\# {\sf SAT}$, yet are widely believed not to admit any Fully Polynomial-time Randomized Approximation Scheme. Recent results reveal a surprising dichotomy in the behavior of $\#{\sf BIS}$: it admits a Fully Polynomial-Time Approximation Scheme (FPTAS) for graphs of max degree $\le 5$~\citep{Weitz2006}, but is as hard to approximate as the general $\#{\sf BIS}$ problem on graphs of degree $\ge 6$~\citep{Cai2016}. In other words, there is a clear threshold, in term of the max degree, separating (relatively) easy instances from really hard ones.

@@

@@
